Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-20 article_review/reviewer_letter.tex
added Section 5.3, reworked Section 5.2, deleted c_j figures

{\color{blue} The new academic application is in dimension $10$. For higher-dimensional examples, we expect the effective dimension to be much smaller than its nominal dimension. Otherwise, a high dimensional problem with high effective dimension will be hard to deal with in most applications. In low effective dimensional problems, most Sobol' indices will have a small value. As shown in the examples, all the small value indices are very easily estimated. Furthermore, the estimator ``Correlation 2'' can (in some cases) reduce further the function values needed for inputs with small main effects.}
\end{itemize}

@@

To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the Bratley test function in Section 5.3. Results show that for an equivalent number of evaluations, random methods using confidence intervals are less accurate than our procedure.}

@@

{\color{blue} The ``real case model'' has been replaced with a new one suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
\end{itemize}

@@

Nonetheless, we modified the definition to only consider point sets whose points are coordinate-wise different. More precisely, consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\vx_{i_1}$, $\vx_{i_2}$, two different points from this set. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This solves the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.

Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case: $\forall i, \ \vx'_i=\vx_i$.}

@@

Since evaluating the effective dimension is not in the scope of this paper, we propose the following. The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension. Then, this assumption is tested on each example by plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function. Our results are compared to older results obtained by screening approaches (Moon, H. (2010)).}

>>>>

{\color{blue} The new academic application is in dimension $15$. For higher-dimensional examples, we expect the effective dimension to be much smaller than its nominal dimension. Otherwise, a high dimensional problem with high effective dimension will be hard to deal with in most applications. In low effective dimensional problems, most Sobol' indices will have a small value. As shown in the examples, all the small value indices are very easily estimated. Furthermore, the estimator ``Correlation 2'' can (in some cases) reduce further the function values needed for inputs with small main effects.}
\end{itemize}

@@

To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the bratley \textit{et al.} test function in Section 5.3. Results show that for an equivalent number of evaluations, the random sampling method is less accurate than our procedure.}

@@

{\color{blue} The ``real case model'' has been replaced with a new application as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
\end{itemize}

@@

Nonetheless, we modified the definition to only consider point sets whose points are coordinate-wise different. More precisely, consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\vx_{i_1}$, $\vx_{i_2}$, two different points from this set. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This solves the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.}

%Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case: $\forall i, \ \vx'_i=\vx_i$.}

@@

Since evaluating the effective dimension is not in the scope of this paper, we propose the following. The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension. Then, this assumption is tested on each example by comparing the number of evaluations required by each integrand.}
%plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function.} %Our results are compared to older results obtained by screening approaches (Moon, H. (2010)).}
